Analysing Constraint Grammar with a SAT solver

### 2015-10-23 paper/lrec/problem_desc.tex
add more reasons why this is interesting

Constraint Grammar (CG, \cite{karlsson1995constraint})
% \citep[CG][]{karlsson1995constraint} 
is a method for disambiguating morphologically analysed text
% and adding syntactic or dependency labels
. 
A grammar consists of rules that target specific analyses for selection or removal, based on contextual tests. For example, the following rule
\begin{itemize}
\item[] \texttt{REMOVE verb IF (-1C det) ;}
\end{itemize}
removes a verb reading from a word which is preceded by an unambiguously (C) tagged determiner.
Given the following text,
\begin{itemize}
\item[] 
\begin{verbatim}
"<the>"
        "the" det def
"<bear>"
        "bear" noun sg
        "bear" verb pl
\end{verbatim}
\end{itemize}
the rule will match to the word \emph{bear}, and remove the analysis \texttt{verb pl}.
However, if the target word has only one remaining analysis, then the rule will not apply, even if the condition is met.

@@

As CGs grow larger, it gets harder for the grammar writers and users to keep track of all the rules and their interaction.
%\cite{voutilainen2004} gives a detailed account about best practices of grammar writing and efficient use of hand-annotated corpora to aid the grammar development.
%\cite{bick2013tuning} presents a method to optimise hand-written CGs using machine learning techniques.
%Our tools complement the existing methods in CG analysis and optimisation.
%While Bick's experiments show improvements in results, the grammar writer is none the wiser why is the grammar better.
%Authors who have a large hand-annotated corpus can also benefit from our tools.
With our tools, the grammar writer or user can ask specific questions about their grammar, such as:

@@

This technique requires an existing morphological lexicon, but no corpus. 
The lexicon is needed in order to generate realistic ambiguities: e.g. a word can be ambiguous between noun and verb, but not between adjective and punctuation. 
Constraints for the structure of the sequences come from the CG rules themselves.
We encode both of these constraints as a satisfiability problem, and use a SAT solver to generate answers to the previous questions.

>>>>

Constraint Grammar (CG, \cite{karlsson1995constraint})
% \citep[CG][]{karlsson1995constraint} 
is a formalism used to disambiguate morphologically analysed text
% and adding syntactic or dependency labels
. 
A grammar consists of rules that target specific analyses for selection or removal, based on contextual tests. For example, the following rule
\begin{itemize}
\item[] \texttt{REMOVE verb IF (-1C det) ;}
\end{itemize}
removes a verb reading from a word which is preceded by an unambiguously (C) tagged determiner.
Given the following text,
\begin{itemize}
\item[] 
\begin{verbatim}
"<the>"
        "the" det def
"<bear>"
        "bear" noun sg
        "bear" verb pl
\end{verbatim}
\end{itemize}
the rule will match to the word \emph{bear}, and remove the analysis \texttt{verb pl}.
However, if the target word has only one remaining analysis, then the rule will not apply, even if the condition is met.

@@

As CGs grow larger, it gets harder for the grammar writers and users to keep track of all the rules and their interaction.
%\cite{voutilainen2004} gives a detailed account about best practices of grammar writing and efficient use of hand-annotated corpora to aid the grammar development.
%\cite{bick2013tuning} presents a method to optimise hand-written CGs using machine learning techniques.
%Our tools complement the existing methods in CG analysis and optimisation.
%While Bick's experiments show improvements in results, the grammar writer is none the wiser why is the grammar better.
%Authors who have a large hand-annotated corpus can also benefit from our tools.
With our tools, the users can diagnose and improve their grammars.
We can ask specific questions about a given grammar, such as:

@@

Our technique requires an existing morphological lexicon, but no corpus. 
The lexicon is needed in order to generate realistic ambiguities: e.g. a word can be ambiguous between noun and verb, but not between adjective and punctuation. 
Constraints for the structure of the sequences come from the CG rules themselves.
We encode both of these constraints as a satisfiability problem, and use a SAT solver to generate answers to the previous questions.
